### 2018-10-06 Chapters/Chapter2.tex
order

\begin{equation}
\boldsymbol{S}_i = \frac{1}{2} \sum_{\sigma, \sigma'} \hat{c}_{i \sigma}^\dagger \boldsymbol{\sigma}_{\sigma, \sigma'} \hat{c}_{i \sigma'}
\end{equation}

@@

\begin{align*}
\hat{c}_{i \sigma}^\dagger \hat{c}_{i \sigma'} &= \delta_{\sigma \sigma'} \frac{1}{2} (n_{i \uparrow} + n_{i \downarrow}) + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma', \sigma} \\ 
\hat{c}_{i \sigma} \hat{c}_{i \sigma'}^\dagger &= \delta_{\sigma \sigma'} \frac{1}{2} (2 - n_{i \uparrow} - n_{i \downarrow}) - \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma, \sigma'} 
\end{align*}

Introducing these relations into $\hat{H}_J$ and using $n_{i \uparrow} + n_{i \downarrow} = 1$ we obtain:

\begin{align*}
\hat{H}_{J} = &-\frac{t^2}{\text{U}} \sum_{\langle i,j \rangle, \sigma \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma \sigma'}\right) = \\
&-\frac{t^2}{\text{U}}\sum_{\langle i,j \rangle, \sigma \sigma'} \left\{ \frac{1}{4}\delta_{\sigma \sigma'} - \sum_{ab} S_i^aS_j^b 	\boldsymbol{\sigma}_{\sigma'\sigma}^a \boldsymbol{\sigma}_{\sigma \sigma'}^b \right\} = 
-\frac{t^2}{\text{U}}\sum_{\langle i,j \rangle} \left\{ \frac{1}{2} - \sum_{ab} S_i^aS_j^b	2\delta_{ab} \right\} = \\
&-\frac{t^2}{\text{U}}\sum_{\langle i,j \rangle} \left( \frac{1}{2} - 2\boldsymbol{S}_i\boldsymbol{S}_j \right)
\end{align*}

@@

Which is the Heisenberg model for antiferromagnets with $J = \frac{2t^2}{\text{U}} > 0$. Likewise, for $\hat{H}_D$:

\begin{align*}
\hat{H}_D = &-\frac{t}{\text{U}} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4}\boldsymbol{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}\boldsymbol{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \boldsymbol{\sigma}_{\sigma_3\sigma_4})\left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma_2 \sigma_3}\right) = \\
 &= -\frac{t}{\text{U}} \sum_{\langle i,j \rangle} \left\{ \right.
	\overbrace{0}^{\uparrow \uparrow \uparrow \uparrow} +
	\overbrace{(-\Delta_{ij}^+)S_i^-(\frac{1}{2}-S_j^z)}^{\uparrow \uparrow \uparrow \downarrow} +
	\overbrace{(-\Delta_{ij}^-)(\frac{1}{2}+ S_i^z)(-S_j^+)}^{\uparrow \uparrow \downarrow \uparrow} +
	\overbrace{2\Delta_{ij}^z S_i^-(-S_j^+)}^{\uparrow \uparrow \downarrow \downarrow} + \\
	&\overbrace{\Delta_{ij}^+ (\frac{1}{2}+S_i^z)(-S_j^-)}^{\uparrow \downarrow \uparrow \uparrow} +
	\overbrace{0}^{\uparrow \downarrow \uparrow \downarrow} +
	\overbrace{0}^{\uparrow \downarrow \downarrow \uparrow} +
	\overbrace{\Delta_{ij}^+ S_i^-(\frac{1}{2}+S_j^z)}^{\uparrow \downarrow \downarrow \downarrow} + \\
	&\overbrace{\Delta_{ij}^- S_i^+(\frac{1}{2}-S_j^z)}^{\downarrow \uparrow \uparrow \uparrow} +
	\overbrace{0}^{\downarrow \uparrow \uparrow \downarrow} +
	\overbrace{0}^{\downarrow \uparrow \downarrow \uparrow} +
	\overbrace{\Delta_{ij}^- (\frac{1}{2} - S_i^z) (-S_j^+)}^{\downarrow \uparrow \downarrow \downarrow} + \\
	& \overbrace{(-2\Delta_{ij}^z)S_i^+(-S_j^-)}^{\downarrow \downarrow \uparrow \uparrow} +
	\overbrace{(-\Delta_{ij}^+) (\frac{1}{2}-S_i^z)(-S_j^-)}^{\downarrow \downarrow \uparrow \downarrow} +
	\overbrace{(-\Delta_{ij}^-) S_i^+(\frac{1}{2}+S_j^z)}^{\downarrow \downarrow \downarrow \uparrow} +
	\overbrace{0}^{\downarrow \downarrow \downarrow \downarrow}
\left. \right\} = \\
&= -\frac{2t}{\text{U}}\sum_{\langle i,j \rangle}\left\{ \Delta_{ij}^+ (S_i^-S_j^z - S_i^zS_j^-) + \Delta_{ij}^- (S_i^zS_j^+ - S_i^+S_j^z) + \Delta_{ij}^z (S_i^+S_j^- - S_i^-S_j^+) \right\} = \\
&= +\frac{2ti}{\text{U}}\sum_{\langle i,j \rangle}\left\{ \Delta_{ij}^+ (\bs{S}_i\times\bs{S}_j)^- + \Delta_{ij}^- (\bs{S}_i\times\bs{S}_j)^+ + 2\Delta_{ij}^z (\bs{S}_i\times\bs{S}_j)^z \right\} = \\
&= +\frac{4it}{\text{U}} \sum_{\langle i,j \rangle} \boldsymbol{\Delta}_{ij} \boldsymbol{S}_i \times \boldsymbol{S}_j = \sum_{\langle i,j \rangle} \boldsymbol{D}_{ij} \boldsymbol{S}_i \times \boldsymbol{S}_j
\end{align*}

In the second line we expand the sum in the spin states (overbrace indicates the spin state $\sigma_1$, $\sigma_2$, $\sigma_3$, $\sigma_4$ respectively). We also used that for any vector $\vec{v}$ we can define $\bs{\sigma}_{12}\vec{v} = v^x+iv^y = v^+$, $\bs{\sigma}_{21}\vec{v} = v^x-iv^y = v^-$, $\bs{\sigma}_{11}\vec{v} = v^z$ and $\bs{\sigma}_{22}\vec{v} = -v^z$. Also, for any two vectors $\vec{a}$ and $\vec{b}$, the following applies $a^-b^z-a^zb^- = -i(\vec{a}\times\vec{b})^-$, $a^zb^+-a^+b^z=-i(\vec{a}\times\vec{b})^+$, $a^+b^--a^-b^+=-2i(\vec{a}\times \vec{b})^z$ and $a^+b^-+a^-b^+=2(a^xb^x+a^yb^y)$.
Where $\boldsymbol{D}_{ij} = \frac{4it}{\text{U}}\boldsymbol{\Delta}_{ij}$. The total effective Hamiltonian is:

\begin{equation}
\hat{H}_{eff} = \sum_{\langle i,j \rangle} J\boldsymbol{S}_i\boldsymbol{S}_j + \boldsymbol{D}_{ij} \boldsymbol{S}_i \times \boldsymbol{S}_j
\end{equation}

>>>>

\begin{equation}
\label{SpinOperators}
\boldsymbol{S}_i = \frac{1}{2} \sum_{\sigma, \sigma'} \hat{c}_{i \sigma}^\dagger \boldsymbol{\sigma}_{\sigma, \sigma'} \hat{c}_{i \sigma'}
\end{equation}

@@

\begin{align}
\hat{c}_{i \sigma}^\dagger \hat{c}_{i \sigma'} &= \delta_{\sigma \sigma'} \frac{1}{2} (n_{i \uparrow} + n_{i \downarrow}) + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma', \sigma} \label{SpinOperatorInv1}\\ 
\hat{c}_{i \sigma} \hat{c}_{i \sigma'}^\dagger &= \delta_{\sigma \sigma'} \frac{1}{2} (2 - n_{i \uparrow} - n_{i \downarrow}) - \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma, \sigma'} \label{SpinOperatorInv2}
\end{align}

In the half-filling case we have $n_{i \uparrow} + n_{i \downarrow} = 1$ and we can show two important relations. First:

\begin{align*}
&\sum_{\sigma \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma \sigma'}\right) = \sum_{\sigma \sigma'} \left\{ \frac{1}{4}\delta_{\sigma \sigma'} - \sum_{ab} S_i^aS_j^b 	\boldsymbol{\sigma}_{\sigma'\sigma}^a \boldsymbol{\sigma}_{\sigma \sigma'}^b \right\}= \\
&= \frac{1}{2} - \sum_{ab} S_i^aS_j^b	2\delta_{ab} = \frac{1}{2} - 2\boldsymbol{S}_i\boldsymbol{S}_j
\end{align*}

Where we have neglected the term $\sum_{\sigma \sigma'} \frac{1}{2}\delta_{\sigma,\sigma'}(\bs{S}_i\bs{\sigma}_{\sigma',\sigma} - \bs{S}_j\bs{\sigma}_{\sigma,\sigma'})$ because eventually we will sum over all $\langle i, j \rangle$ and it will cancel out. We also used the well known property $tr(\bs{\sigma}^a\bs{\sigma}^b)=2\delta_{a,b}$. And second:

\begin{align*}
&\sum_{\sigma_1, \sigma_2, \sigma_3, \sigma_4}\boldsymbol{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}\boldsymbol{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \boldsymbol{\sigma}_{\sigma_3\sigma_4})\left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma_2 \sigma_3}\right) = \\
 &= \left\{ \right.
	\overbrace{0}^{\uparrow \uparrow \uparrow \uparrow} +
	\overbrace{(-\Delta_{ij}^+)S_i^-(\frac{1}{2}-S_j^z)}^{\uparrow \uparrow \uparrow \downarrow} +
	\overbrace{(-\Delta_{ij}^-)(\frac{1}{2}+ S_i^z)(-S_j^+)}^{\uparrow \uparrow \downarrow \uparrow} +
	\overbrace{2\Delta_{ij}^z S_i^-(-S_j^+)}^{\uparrow \uparrow \downarrow \downarrow} + \\
	&\overbrace{\Delta_{ij}^+ (\frac{1}{2}+S_i^z)(-S_j^-)}^{\uparrow \downarrow \uparrow \uparrow} +
	\overbrace{0}^{\uparrow \downarrow \uparrow \downarrow} +
	\overbrace{0}^{\uparrow \downarrow \downarrow \uparrow} +
	\overbrace{\Delta_{ij}^+ S_i^-(\frac{1}{2}+S_j^z)}^{\uparrow \downarrow \downarrow \downarrow} + \\
	&\overbrace{\Delta_{ij}^- S_i^+(\frac{1}{2}-S_j^z)}^{\downarrow \uparrow \uparrow \uparrow} +
	\overbrace{0}^{\downarrow \uparrow \uparrow \downarrow} +
	\overbrace{0}^{\downarrow \uparrow \downarrow \uparrow} +
	\overbrace{\Delta_{ij}^- (\frac{1}{2} - S_i^z) (-S_j^+)}^{\downarrow \uparrow \downarrow \downarrow} + \\
	& \overbrace{(-2\Delta_{ij}^z)S_i^+(-S_j^-)}^{\downarrow \downarrow \uparrow \uparrow} +
	\overbrace{(-\Delta_{ij}^+) (\frac{1}{2}-S_i^z)(-S_j^-)}^{\downarrow \downarrow \uparrow \downarrow} +
	\overbrace{(-\Delta_{ij}^-) S_i^+(\frac{1}{2}+S_j^z)}^{\downarrow \downarrow \downarrow \uparrow} +
	\overbrace{0}^{\downarrow \downarrow \downarrow \downarrow}
\left. \right\} = \\
&= 2\left\{ \Delta_{ij}^+ (S_i^-S_j^z - S_i^zS_j^-) + \Delta_{ij}^- (S_i^zS_j^+ - S_i^+S_j^z) + \Delta_{ij}^z (S_i^+S_j^- - S_i^-S_j^+) \right\} = \\
&= -2i\left\{ \Delta_{ij}^+ (\bs{S}_i\times\bs{S}_j)^- + \Delta_{ij}^- (\bs{S}_i\times\bs{S}_j)^+ + 2\Delta_{ij}^z (\bs{S}_i\times\bs{S}_j)^z \right\} = -4i \boldsymbol{\Delta}_{ij} \boldsymbol{S}_i \times \boldsymbol{S}_j 
\end{align*}

Where in the second line we expand the sum in the spin states (overbrace indicates the spin state $\sigma_1$, $\sigma_2$, $\sigma_3$, $\sigma_4$ respectively). We also used that for any vector $\vec{v}$ we can define $\bs{\sigma}_{12}\vec{v} = v^x+iv^y = v^+$, $\bs{\sigma}_{21}\vec{v} = v^x-iv^y = v^-$, $\bs{\sigma}_{11}\vec{v} = v^z$ and $\bs{\sigma}_{22}\vec{v} = -v^z$. Also, for any two vectors $\vec{a}$ and $\vec{b}$, the following applies $a^-b^z-a^zb^- = -i(\vec{a}\times\vec{b})^-$, $a^zb^+-a^+b^z=-i(\vec{a}\times\vec{b})^+$, $a^+b^--a^-b^+=-2i(\vec{a}\times \vec{b})^z$ and $a^+b^-+a^-b^+=2(a^xb^x+a^yb^y)$.

These two relations are important and will be used in the next chapter:

\begin{align}
&\sum_{\sigma \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma \sigma'}\right) =\frac{1}{2} - \sum_{ab} S_i^aS_j^b	2\delta_{ab} = \frac{1}{2} - 2\boldsymbol{S}_i\boldsymbol{S}_j \label{SpinRel1} \\
&\sum_{\sigma_1, \sigma_2, \sigma_3, \sigma_4}\boldsymbol{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}\boldsymbol{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \boldsymbol{\sigma}_{\sigma_3\sigma_4})\left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma_2 \sigma_3}\right)= -4i \boldsymbol{\Delta}_{ij} \boldsymbol{S}_i \times \boldsymbol{S}_j \label{SpinRel2}
\end{align}

Now introducing the spin operators into  $\hat{H}_J$ with $n_{i \uparrow} + n_{i \downarrow} = 1$ and using \ref{SpinRel1} we obtain:

\begin{align*}
\hat{H}_{J} = &-\frac{t^2}{\text{U}} \sum_{\langle i,j \rangle, \sigma \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma \sigma'}\right) = \\
&-\frac{t^2}{\text{U}}\sum_{\langle i,j \rangle} \left( \frac{1}{2} - 2\boldsymbol{S}_i\boldsymbol{S}_j \right)
\end{align*}

@@

Which is the Heisenberg model for antiferromagnets with $J = \frac{2t^2}{\text{U}} > 0$. Likewise, for $\hat{H}_D$, using \ref{SpinRel2}:

\begin{align*}
\hat{H}_D = &-\frac{t}{\text{U}} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4}\boldsymbol{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}\boldsymbol{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \boldsymbol{\sigma}_{\sigma_3\sigma_4})\left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma_2 \sigma_3}\right) = \\
&= +\frac{4it}{\text{U}} \sum_{\langle i,j \rangle} \boldsymbol{\Delta}_{ij} \boldsymbol{S}_i \times \boldsymbol{S}_j = \sum_{\langle i,j \rangle} \boldsymbol{D}_{ij} \boldsymbol{S}_i \times \boldsymbol{S}_j
\end{align*}

Where $\boldsymbol{D}_{ij} = \frac{4it}{\text{U}}\boldsymbol{\Delta}_{ij}$. The total effective Hamiltonian is:

\begin{equation}
\hat{H}_{eff} = \sum_{\langle i,j \rangle} \left( J\boldsymbol{S}_i\boldsymbol{S}_j + \boldsymbol{D}_{ij} \boldsymbol{S}_i \times \boldsymbol{S}_j \right)
\end{equation}

### 2018-10-06 Chapters/Chapter3.tex
Contituum ham
order

\begin{section}{Modified exchange interaction}

@@

Where $t_{ij,m} = t_0 e^{i(\frac{\pi}{2}-\theta_{ij})m} J_m(\alpha_{ij})$ and $J_m(x)$ is the \textit{m}th Bessel function. Correspondingly $\hat{T}(t) = \sum_m \hat{T}_m e^{im \omega t}$.

@@

>>>>

\begin{section}{Hubbard model without SOI}

@@

Where $t_{ij,m} = t_0 e^{i(\frac{\pi}{2}-\theta_{ij})m} J_m(\alpha_{ij})$ and $J_m(x)$ is the \textit{m}th Bessel function \cite{Kitamura2017}. Correspondingly $\hat{T}(t) = \sum_m \hat{T}_m e^{im \omega t}$.

@@

\begin{section}{Hubbard model with SOI}

Now, let's investigate the effect of the electric field for the Hubbard model with SOI. As seen in \ref{AP3A} we can use the Peierls substitution to obtain the Hamiltonian:

\begin{equation}
\hat{H}(t) = -\sum_{\langle i,j \rangle, \sigma, \sigma'} e^{ie\bs{R}_{ij}\bs{A}(t)} (\delta_{\sigma \sigma'}t_0 + \bs{\Delta}_{ij}\bs{\sigma}_{\sigma \sigma'}) \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow} = -\hat{T}(t) + \text{U}\hat{D}
\end{equation}

In this case the hopping operator $\hat{T}(t)$ includes the spin orbit interaction, but the time dependence is the same as before, we can use $e^{ie\bs{R}_{ij}\bs{A}(t)} =  \sum_m e^{i(\frac{\pi}{2}-\theta_{ij})m} J_m(\alpha_{ij}) e^{im\omega t}$ where as before $e\bs{R}_{ij}\vec{A} = \alpha_{ij} e^{i \theta_{ij}}$ to write:

\begin{equation}
\hat{T}(t) = \sum_{\langle i,j \rangle, \sigma, \sigma'} \sum_m \Gamma_{ij,m}^{\sigma\sigma'} e^{im \omega t} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}
\end{equation}

Where we define $\Gamma_{ij,m}^{\sigma\sigma'} = e^{i(\frac{\pi}{2}-\theta_{ij})m} J_m(\alpha_{ij})(\delta_{\sigma, \sigma'}t_0+\bs{\Delta}_{ij}\bs{\sigma}_{\sigma \sigma'})$ a scalar. Now we can follow the same procedure as in the previous section to obtain:

\begin{equation}
\hat{H}'^{(2)}(t) = \sum_{mn} \left( \frac{\left[\hat{T}_{1n}, \hat{T}_{-1(m-n)} \right]}{\text{U}+n\omega} - \frac{\left[\hat{T}_{-1n}, \hat{T}_{1(m-n)} \right]}{\text{U}-n\omega} \right) e^{im\omega t}
\end{equation}

As before, we are only interested on how the Hamiltonian acts on the subspace of doublon number $d=0$. In that subspace we have:

\begin{equation}
\hat{H}_{eff}(t) = \hat{P}_0 \hat{H}'^{(2)}(t)\hat{P}_0 = - \sum_{mn} \left( \frac{\hat{T}_{-1(m-n)}\hat{T}_{1n}  }{\text{U}+n\omega} + \frac{\hat{T}_{-1n}\hat{T}_{1(m-n)}}{\text{U}-n\omega} \right) e^{im\omega t}
\end{equation}

Where,

\begin{equation}
\hat{P}_0 \hat{T}_{-1a}\hat{T}_{1b} \hat{P}_0 = \sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \Gamma_{ij,a}^{\sigma_1\sigma_2}\Gamma_{ji,b}^{\sigma_3\sigma_4} \hat{c}_{i\sigma_1}^\dagger\hat{c}_{j\sigma_2}\hat{c}_{j\sigma_3}^\dagger\hat{c}_{i\sigma_4}
\end{equation}

For any integers $a,b$. Therefore:

\begin{equation}
\hat{H}_{eff}(t) = -\sum_{mn} \sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \hat{c}_{i\sigma_1}^\dagger\hat{c}_{j\sigma_2}\hat{c}_{j\sigma_3}^\dagger\hat{c}_{i\sigma_4} \left\{ \frac{\Gamma_{ij,(m-n)}^{\sigma_1\sigma_2}\Gamma_{ji,n}^{\sigma_3\sigma_4}}{\text{U}+n\omega} + \frac{\Gamma_{ij,n}^{\sigma_1\sigma_2}\Gamma_{ji,(m-n)}^{\sigma_3\sigma_4}}{\text{U}-n\omega} \right\} e^{im\omega t}
\end{equation}

We can rewrite:

\begin{align*}
\Gamma_{ij,(m-n)}^{\sigma_1\sigma_2}\Gamma_{ji,n}^{\sigma_3\sigma_4} &= e^{i(\frac{\pi}{2}-\theta_{ij})m}J_{m-n}(\alpha_{ij})J_n(\alpha_{ji})(\delta_{\sigma_1, \sigma_2}t_0+\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\delta_{\sigma_3, \sigma_4}t_0+\bs{\Delta}_{ji}\bs{\sigma}_{\sigma_3 \sigma_4}) = \\
&= e^{i(\frac{\pi}{2}-\theta_{ij})m}J_{m-n}(\alpha_{ij})J_{-n}(\alpha_{ij})(\delta_{\sigma_1, \sigma_2}t_0+\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\delta_{\sigma_3, \sigma_4}t_0-\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_3 \sigma_4}) = \\
&= e^{i(\frac{\pi}{2}-\theta_{ij})m}J_{m-n}(\alpha_{ij})J_{-n}(\alpha_{ij}) \left[ \delta_{\sigma_1, \sigma_2}\delta_{\sigma_3, \sigma_4}t_0^2+t_0\bs{\Delta}_{ij}(\delta_{\sigma_3,\sigma_4}\bs{\sigma}_{\sigma_1 \sigma_2}-\delta_{\sigma_1,\sigma_2}\bs{\sigma}_{\sigma_3 \sigma_4}) + \mathcal{O}(\bs{\Delta}_{ij}^2) \right]
\end{align*}

Where we used $\theta_{ji} = \theta_{ij}$, $\alpha_{ji} = - \alpha_{ij}$ and $\bs{\Delta}_{ji} = -\bs{\Delta}_{ij}$. We neglect the $\mathcal{O}(\bs{\Delta}_{ij}^2)$ term. The term proportional to $t_0^2$ will lead to the modified exchange interaction, and it is exactly the same as in the previous section. The term proportional to $t_0\bs{\Delta}_{ij}$ will lead to the modified DMI interaction. Define:

\begin{equation}
\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) = \sum_{mn}e^{i(\frac{\pi}{2}-\theta_{ij})m} \left\{ 
    \frac{J_{m-n}(\alpha_{ij})J_{-n}(\alpha_{ij})}{\text{U}+n\omega} +
    \frac{J_n(\alpha_{ij})J_{n-m}(\alpha_{ij})}{\text{U}-n\omega}    
    \right\}e^{im\omega t}
\end{equation}

Now, introducing the spin operators \ref{SpinOperators}, using relations \ref{SpinOperatorInv1} and \ref{SpinOperatorInv2} and taking into account that in this subspace $n_{i\uparrow}+n_{i\downarrow}=1$ we obtain:

\begin{align*}
\hat{H}_{eff}(t) &\approx -\sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) \times \\
&\times \left[ \delta_{\sigma_1, \sigma_2}\delta_{\sigma_3, \sigma_4}t_0^2+t_0\bs{\Delta}_{ij}(\delta_{\sigma_3,\sigma_4}\bs{\sigma}_{\sigma_1 \sigma_2}-\delta_{\sigma_1,\sigma_2}\bs{\sigma}_{\sigma_3 \sigma_4}) \right]\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) = \\
&= -t_0^2 \sum_{\langle i,j \rangle \sigma, \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \bs{S}_i\bs{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\bs{S}_j\bs{\sigma}_{\sigma \sigma'}\right)\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) - \\
&- t_0 \sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) \times \\
&\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \bs{\Delta}_{ij}(\delta_{\sigma_3,\sigma_4}\bs{\sigma}_{\sigma_1 \sigma_2}-\delta_{\sigma_1,\sigma_2}\bs{\sigma}_{\sigma_3 \sigma_4}) = \\
&= \hat{H}_J'(t)+\hat{H}_D'(t)
\end{align*}

Now, for $\hat{H}_J'(t)$ we know from the previous chapter that:

\begin{equation}
\sum_{\langle i,j \rangle \sigma, \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \bs{S}_i\bs{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\bs{S}_j\bs{\sigma}_{\sigma \sigma'}\right) = -2\sum_{\langle i,j \rangle}\bs{S}_i\bs{S}_j
\end{equation}

Up to a constant. Therefore:

\begin{align}
\hat{H}_J'(t) &= 2t_0^2 \sum_{mn} \bs{S}_i\bs{S}_j e^{i(\frac{\pi}{2}-\theta_{ij})m} \left\{ 
    \frac{J_{m-n}(\alpha_{ij})J_{-n}(\alpha_{ij})}{\text{U}+n\omega} +
    \frac{J_n(\alpha_{ij})J_{n-m}(\alpha_{ij})}{\text{U}-n\omega}    
    \right\}e^{im\omega t} = \nonumber \\
&= \sum_{mn} \bs{S}_i\bs{S}_j J_{ij}(t)
\end{align}

With the same expression for $J_{ij}(t)$ as in the previous section. For $\hat{H}_D'(t)$ we use the relation:

\begin{align}
&\sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right)\bs{\Delta}_{ij}(\delta_{\sigma_3,\sigma_4}\bs{\sigma}_{\sigma_1 \sigma_2}-\delta_{\sigma_1,\sigma_2}\bs{\sigma}_{\sigma_3 \sigma_4}) = \nonumber \\
&= \sum_{\langle i,j \rangle} 4i\bs{\Delta}_{ij} \bs{S}_i \times \bs{S}_j
\end{align}

To obtain:

\begin{equation}
\hat{H}_D'(t) = -\sum_{\langle i,j \rangle} 4it_0 \bs{\Delta}_{ij}\mathcal{M}(\alpha_{ij},t) \bs{S}_i \times \bs{S}_j = \sum_{\langle i,j \rangle} \bs{D}_{ij}(t) \bs{S}_i \times \bs{S}_j
\end{equation}

\begin{equation}
\bs{D}_{ij} = -4it_0\bs{\Delta}_{ij}\mathcal{M}(\alpha_{ij},t) = -4it_0 \bs{\Delta}_{ij} \sum_{mn}e^{i(\frac{\pi}{2}-\theta_{ij})m} \left\{ 
    \frac{J_{m-n}(\alpha_{ij})J_{-n}(\alpha_{ij})}{\text{U}+n\omega} +
    \frac{J_n(\alpha_{ij})J_{n-m}(\alpha_{ij})}{\text{U}-n\omega}    
    \right\}e^{im\omega t}
\end{equation}
